### 2024-07-19 doc/example.tex
Update examples

Litrepl uses its own internal parser to determine LaTeX-looking tags defining
code and result sections. As one option, it expects \texttt{python} environment
to mark code and \texttt{result} wrapping results. Both tags need to be
introduced to LaTeX so it doesn't get confused. The following preamble sets both
environments to be rendered as framed boxes of fixed-width text with proper
highlighting:

@@

@@

Putting the cursor on it and typing the \texttt{:LEval} runs the code in the
background Python interpreter.

\texttt{result} begin/end tags mark the result section.  LitREPL replaces its
content with the above code section's execution result.

@@

LitREPL also recognizes \texttt{result}/\texttt{noresult} comments as result
section markers. With their help we can directly produce LaTeX markup as output:

@@

Additionally, VimREPL recognises \texttt{linline} 2-argument tags. The first
arguement is treaten as a Python printable expression. The second arguemnt is to
be replaced with its value.

>>>>

Literpl employs its own internal parser to identify LaTeX-like tags that define
code and result sections. One option is to use the \texttt{python} environment
to mark code and wrap results with \texttt{result}. Both environments need to be
defined in LaTeX so it doesn't get confused. The following preamble sets up both
environments to render as framed boxes of fixed-width text with proper
highlighting:

@@

Here is how we can use the environments we just introduced.

@@

@@

Literpl also recognizes \texttt{result} and \texttt{noresult} comments, which
serve as markers for result sections. By using these comments, we can generate
LaTeX markup directly as output.

@@

Furthermore, Literpl recognizes \texttt{linline} tags with two arguments. The
first argument is treated as a Python printable expression, while the second
argument will be replaced with its evaluated value.
